Fast and Flexible Binary Instrumentation for the Kernel

### 2013-12-13 VEE-14/paper.tex
Fixes and update of partial specialization subsection.

	\item {\bf It does require any runtime checking of the current runtime context.} If a tool like \toolname{RCUdbg} were implemented with DRK or btkernel, then \toolname{RCUdbg} would need to instrument code to continually check the current context and perform the correct memory access check given the current context. Checking the current context introduces performance overheads (additional instructions must be executed; branch mispredictions), and memory overheads (additional instructions are needed just to figure out what to check; icache misses).

@@

By default, Granary doesn't allow tools to specify policy switches on procedure return instructions (\texttt{ret}). This increases the ``power" of the formal model of policy switching from being a deterministic finite state automaton to being a restricted form of pushdown automaton. The program counter continues to track the current execution state, and saved program counters (returns addresses stored on the runtime call stack) record prior execution states. In this model, \texttt{call}s place contextual breadcrumbs (in the form of return addresses) on the runtime call stack, and \texttt{ret}s read these breadcrumbs to return to a previous context. For many tools, this is a natural model of state tracking as it is bound to both the current thread.

@@

For example, Granary tracks whether code may or may not access user space data, because this code can potentially result in a page fault (\Cref{sec:interrupt_return_address_transparency}). Granary can detect this code using a combination of pattern recognition, and policy property propagation. This internal mechanism is needed for correctly handling page faults in the kernel, and is also useful for optimizing code generated by tools (e.g. \toolname{BoundsChecker}) using Granary's address watchpoints framework \cite{BehaveOrBeWatched}.

>>>>

	\item {\bf It does not require any runtime checking of the current runtime context.} If a tool like \toolname{RCUdbg} were implemented with DRK or btkernel, then \toolname{RCUdbg} would need to instrument code to continually check the current context and perform the correct memory access check given the current context. Checking the current context introduces performance overheads (additional instructions must be executed; branch mispredictions), and memory overheads (additional instructions are needed just to figure out what to check; icache misses).

@@

By default, Granary doesn't allow tools to specify policy switches on procedure return instructions (\texttt{ret}). This increases the ``power" of the formal model of policy switching from being a deterministic finite state automaton to being a restricted form of pushdown automaton. The program counter continues to track the current execution state, and saved program counters (returns addresses stored on the runtime call stack) record prior execution states. In this model, \texttt{call}s place contextual breadcrumbs (in the form of return addresses) on the runtime call stack, and \texttt{ret}s read these breadcrumbs to return to a previous context. For many tools, this is a natural model of state tracking as it is bound to the current thread, and because kernel code tends to follow a good call/return discipline.

@@

For example, Granary tracks whether code may or may not access user space data, because this code can potentially result in a page fault. Granary can detect this code using a combination of pattern recognition, and policy property propagation. This internal mechanism is needed to correctly handle page faults in instrumented kernel code (\Cref{sec:interrupt_return_address_transparency}), and is also useful for optimizing code generated by tools as well. For example, Granary's \toolname{BoundsChecker} tool alters the 16 high order bits of addresses returned from kernel allocators, to make it easy to associate bounds information with each allocated object \cite{BehaveOrBeWatched}. Checked and unchecked kernel addresses can distinguished by testing only a single bit. However, user space addresses and checked addresses are harder to distinguish, requiring two bits to be checked.  Fortunately,  few instructions dereference user space addresses, and Granary tracks whichs basic blocks might contain those instructions, thus allowing the \toolname{BoundsChecker} to avoid many unnecessary bit tests.
